---
title: "SingleCellMQC"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    css: bootstrap.css
    toc: true
    toc_float: 
      collapsed: true      
      smooth_scroll: true  
    number_sections: true
    self_contained: false
#    self_contained: false
params:
  data: out_list
  cell_dir: plot_dir
lang: en
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(echo = TRUE)
```

```{r function, echo=FALSE}
# params:
#   data: out_list
#   cell_dir: plot_dir
subchunkify <- function(g, fig_height=7, fig_width=5, seed=floor(runif(1) * 10000)) {
  g_deparsed <- paste0(deparse(
    function() {g}
  ), collapse = '')

  sub_chunk <- paste0("
  `","``{r sub_chunk_", seed, ", fig.height=",
   fig_height, ", fig.width=", fig_width, ", echo=FALSE, warning=FALSE, message=FALSE}",
  "\n(", 
    g_deparsed
    , ")()",
  "\n`","``
  ")

  cat(knitr::knit(text = knitr::knit_expand(text = sub_chunk), quiet = TRUE))
}

bar_style <- function(width = 1, fill = "#e6e6e6", height = "75%",
                      align = c("left", "right"), color = NULL) {
  align <- match.arg(align)
  if (align == "left") {
    position <- paste0(width * 100, "%")
    image <- sprintf("linear-gradient(90deg, %1$s %2$s, transparent %2$s)", fill, position)
  } else {
    position <- paste0(100 - width * 100, "%")
    image <- sprintf("linear-gradient(90deg, transparent %1$s, %2$s %1$s)", position, fill)
  }
  list(
    backgroundImage = image,
    backgroundSize = paste("100%", height),
    backgroundRepeat = "no-repeat",
    backgroundPosition = "center",
    color = color
  )
}

btn <- function(xLoc, m, nms, xOry, data) { # x btn position, method, names, x or y
  list(type = "list", x = xLoc, xanchor = "left", y = 1.2, 
       buttons = lapply(
         nms, function(k) {           # iterate over names
           list(
             method = m, label = k,
             args = if(xOry == "x"){
               list( # a list for each trace (each legend entry)
                 list(x = list(data[, k] )),  # 3 lists, 3 traces
                 list(xaxis = list(title = k)))
             }else{
               list(
                 list(y = list(data[, k] )),  # 3 lists, 3 traces
                 list(yaxis = list(title = k)))
             }
           )}
       )
  )}

warning_alert_orange <- function(text) {
  cat(sprintf('<div class="alert alert-warning">
  <h5 class="alert-heading" style="font-size: 20px;" aria-hidden="true">Warning!</h5>
  %s
</div>', text))
}
warning_alert_red <- function(text) {
  cat(sprintf('<div class="alert alert-dismissible alert-danger">
  <h5 class="alert-heading" style="font-size: 20px;" aria-hidden="true">Warning!</h5>
  %s
</div>', text))
}

note_grey <- function(text) {
  cat(sprintf('<div class="alert alert-dismissible alert-light">
  %s
</div>', text))
}



data <- params$data
cell_dir <- params$cell_dir

```


```{r Sample QC, echo=FALSE, results='asis'}
if (!is.null(data$Sample)) {
  cat(knitr::knit_child("Sample_QC.Rmd", quiet = TRUE))
  cat("\n\n")
}
```

```{r Cell QC, echo=FALSE, results='asis'}
if (!is.null(data$Cell)) {
  cat(knitr::knit_child("Cell_QC.Rmd", quiet = TRUE))
    cat("\n\n")

}
```

```{r Feature QC, echo=FALSE, results='asis'}
if (!is.null(data$Feature)) {
  cat(knitr::knit_child("Feature_QC.Rmd", quiet = TRUE))
    cat("\n\n")

}
```

```{r Batch QC, echo=FALSE, results='asis'}
if (!is.null(data$Batch)) {
  cat(knitr::knit_child("Batch_QC.Rmd", quiet = TRUE))
    cat("\n\n")

}
```


# Abbreviations {.tabset .unnumbered}
## Sample metrics {.tabset -}
### Common {-}
- **nCell** — Total number of cells captured for each sample.
- **nGene_RNA** — Number of genes detected in each sample.
- **nPro_ADT** — Number of protein targets quantified by antibody-derived tags (ADT) in each sample.
- **nChain_TCR** — Total number of T-cell receptor (TCR) chains detected in each sample.
- **nCell_TCR** — Number of cells with detected TCR chains in each sample.
- **TCR%** — Percentage of cells with detected TCR chains relative to total cells in each sample.
- **nChain_BCR** — Total number of B-cell receptor (BCR) chains detected in each sample.
- **nCell_BCR** — Number of cells with detected BCR chains in each sample.
- **BCR%** — Percentage of cells with detected BCR chains relative to total cells in each sample.
- **nChain_TRA** — Total number of TCR alpha chains detected in each sample.
- **nCell_TRA** — Number of cells with detected TCR alpha chains in each sample.
- **TRA%** — Percentage of cells with detected TCR alpha chains relative to total cells in each sample.
- **nChain_TRB** — Total number of TCR beta chains detected in each sample.
- **nCell_TRB** — Number of cells with detected TCR beta chains in each sample.
- **TRB%** — Percentage of cells with detected TCR beta chains relative to total cells in each sample.
- **nChain_IGH** — Total number of immunoglobulin heavy (IGH) chains detected in each sample.
- **nCell_IGH** — Number of cells with detected IGH chains in each sample.
- **IGH%** — Percentage of cells with detected IGH chains relative to total cells in each sample.
- **nChain_IGK** — Total number of immunoglobulin kappa (IGK) light chains detected in each sample.
- **nCell_IGK** — Number of cells with detected IGK chains in each sample.
- **IGK%** — Percentage of cells with detected IGK chains relative to total cells in each sample.
- **nChain_IGL** — Total number of immunoglobulin lambda (IGL) light chains detected in each sample.
- **nCell_IGL** — Number of cells with detected IGL chains in each sample.
- **IGL%** — Percentage of cells with detected IGL chains relative to total cells in each sample.

### V(D)J subtype {-}
- **IGH + IGK** — Total number of cells with detected IGH and IGK chains.
- **IGH + IGL** — Total number of cells with detected IGH and IGL chains.
- **TRA + TRB** — Total number of cells with detected TRA and TRB chains.
- **ambiguous_TB** — Number of cells with both TCR and BCR chains detection.
- **multichain_B** — Number of cells with multiple BCR chains detected (2 or more IGH chains and/or 2 or more IGK/L chains).
- **multichain_T** — Number of cells with multiple TCR chains detected (2 or more TRA chains and/or 2 or more TRB chains).
- **single IGH** — Number of cells with only a single detected IGH chain.
- **single IGK** — Number of cells with only a single detected IGK chain.
- **single IGL** — Number of cells with only a single detected IGL chain.
- **single TRA** — Number of cells with only a single detected TRA chain.
- **single TRB** — Number of cells with only a single detected TRB chain.
- **IGH + IGK%** — Percentage of cells with both IGH and IGK chains relative to total cells.
- **IGH + IGL%** — Percentage of cells with both IGH and IGL chains relative to total cells.
- **TRA + TRB%** — Percentage of cells with both TRA and TRB chains relative to total cells.
- **ambiguous_TB%** — Percentage of cells with both TCR and BCR chains detection relative to total cells.
- **multichain_B%** — Percentage of cells with multiple BCR chains (2 or more IGH chains and/or 2 or more IGK/L chains) relative to total cells.
- **multichain_T%** — Percentage of cells with multiple TCR chains (2 or more TRA chains and/or 2 or more TRB chains) relative to total cells.
- **single IGH%** — Percentage of cells with only a single IGH chain relative to total cells.
- **single IGK%** — Percentage of cells with only a single IGK chain relative to total cells.
- **single IGL%** — Percentage of cells with only a single IGL chain relative to total cells.
- **single TRA%** — Percentage of cells with only a single TRA chain relative to total cells.
- **single TRB%** — Percentage of cells with only a single TRB chain relative to total cells.

## Cell metrics {-}

- **nCount_RNA** — Total number of unique molecular identifiers (UMIs) detected in each cell.
- **nFeature_RNA** — Number of unique genes detected in each cell.
- **nCount_ADT** — Total number of unique molecular identifiers (UMIs) associated with antibody-derived tags in each cell.
- **nFeature_ADT** — Number of unique ADT features detected in each cell.
- **percent.mt** — Percentage of mitochondrial transcripts out of the total RNA transcripts in each cell.
- **percent.rb** — Percentage of ribosomal transcripts out of total RNA transcripts in each cell.
- **percent.hb** — Percentage of hemoglobin transcripts out of total RNA transcripts in each cell.
- **percent.dissociation** — Percentage of dissociation-related transcripts out of total RNA transcripts in each cell.
- **per_feature_count_RNA** — Average number of UMIs per gene in each cell.
- **per_feature_count_ADT** — Average number of UMIs per ADT feature in each cell.
- **percent.isotype** — Percentage of isotype control antibodies out of total ADTs in each cell.

## Gene/protein metrics { -}

- **nCell** — Number of cells in which a particular feature (e.g., gene or protein) is detected.
- **pct** — Percentage of cells in which a particular feature is detected, relative to the total number of cells analyzed.
- **mean** — Average expression level of a feature (e.g., gene or protein) across all cells in which it is detected.
- **variance** — Statistical measure of the dispersion of a feature's expression levels across cells
- **variance.standardized** — Standardized variance of a feature's expression levels across cells.


# Authors {.unnumbered}

**Wen Lab:**

-  **Daihan Ji**

-  **Mei Han**

-  **Shuting Lu**

-  **Jiaying Zeng** 

-  **Wen Zhong** 


